---
title: "Economic Dashboard"
format: dashboard
server: shiny
---

```{r libs}
#| warning: false 

library(shiny)
library(bslib)
library(tidyverse)
library(ggplot2)
library(gt)
library(rsconnect)
```

```{r palette}

primary <- "#1134A6"
secondary <- "#1e8ad3"
light <- "#d3f4fb"
highlight <- "#10bc10"
white <- "#ffffff"
dark <- "#1d3537"
info <- "#1aa53f"
success <- "#009758"
warning <- "#ddc800"
danger <- "#ea1d00"

```

## Shiny Documents

This Quarto document is made interactive using Shiny. Interactive documents allow readers to modify parameters and see the results immediately. Learn more about Shiny interactive documents at <https://quarto.org/docs/interactive/shiny/>.

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change. This demonstrates how a standard R plot can be made interactive:

```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r}
#| context: server
output$distPlot <- renderPlot({
   x <- faithful[, 2]  # Old Faithful Geyser data
   bins <- seq(min(x), max(x), length.out = input$bins + 1)
   hist(x, breaks = bins, col = 'darkgray', border = 'white',
        xlab = 'Waiting time to next eruption (in mins)',
        main = 'Histogram of waiting times')
})
```
